Capstone Movielens Report

### 2025-11-12 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix.

This function internally uses the [base::union]((https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data into a single data frame for further processing. 
:::

>>>>

This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data list into a single data frame for further processing. 
:::
